Time slice analyses

### 2017-11-27 analyses/01-extract-data-for-analyses.Rmd
Replace save and load with saveRDS and loadRDS, to prevent environment names issues

## Saving the matrix
save(matrix_nodes, file = paste0("../data/processed/ancestral_states.", slug ,".Rda"))
```

@@

```{r}
## Loading the matrix
load(paste0("../data/processed/ancestral_states.", slug ,".Rda"))

@@

## Saving the matrix
save(matrix_dist, file = paste0("../data/processed/distance_matrix.", slug ,".Rda"))
```

@@

## Estimating the ancestral states (with a uncertainty threshold of 0.95)
matrix_nodes <- AncStateEstMatrix(matrix, tree, estimate.allchars = TRUE,
                                  uncertainty.threshold = 0.95)
save(matrix_nodes, file = paste0("../data/processed/ancestral_states.", slug ,".Rda"))

## Add ancestral states to nodes
load(paste0("../data/processed/ancestral_states.", slug ,".Rda"))
row.names(matrix_nodes) <- tree$node.label
matrix$matrix <- rbind(matrix$matrix, matrix_nodes)

## Constructing the distance matrix
matrix_dist <- MorphDistMatrixFast(matrix, distance = "Gower")
save(matrix_dist, file = paste0("../data/processed/distance_matrix.", slug,".Rda"))

@@

## Estimating the ancestral states (with a uncertainty threshold of 0.95)
matrix_nodes <- AncStateEstMatrix(matrix, tree, estimate.allchars = TRUE,
                                  uncertainty.threshold = 0.95)
save(matrix_nodes, file = paste0("../data/processed/ancestral_states.", slug ,".Rda"))

## Add ancestral states to nodes
load(paste0("../data/processed/ancestral_states.", slug ,".Rda"))
row.names(matrix_nodes) <- tree$node.label
matrix$matrix <- rbind(matrix$matrix, matrix_nodes)

## Constructing the distance matrix
matrix_dist <- MorphDistMatrixFast(matrix, distance = "Gower")
save(matrix_dist, file = paste0("../data/processed/distance_matrix.", slug ,".Rda"))
```

>>>>

## Saving the matrix
saveRDS(matrix_nodes, file = paste0("../data/processed/ancestral_states.", slug ,".Rda"))
```

@@

```{r}
## Loading the matrix
readRDS(paste0("../data/processed/ancestral_states.", slug ,".Rda"))

@@

## Saving the matrix
saveRDS(matrix_dist, file = paste0("../data/processed/distance_matrix.", slug ,".Rda"))
```

@@

## Estimating the ancestral states (with a uncertainty threshold of 0.95)
matrix_nodes <- AncStateEstMatrix(matrix, tree, estimate.allchars = TRUE,
                                  uncertainty.threshold = 0.95)
saveRDS(matrix_nodes, file = paste0("../data/processed/ancestral_states.", slug ,".Rda"))

## Add ancestral states to nodes
readRDS(paste0("../data/processed/ancestral_states.", slug ,".Rda"))
row.names(matrix_nodes) <- tree$node.label
matrix$matrix <- rbind(matrix$matrix, matrix_nodes)

## Constructing the distance matrix
matrix_dist <- MorphDistMatrixFast(matrix, distance = "Gower")
saveRDS(matrix_dist, file = paste0("../data/processed/distance_matrix.", slug,".Rda"))

@@

## Estimating the ancestral states (with a uncertainty threshold of 0.95)
matrix_nodes <- AncStateEstMatrix(matrix, tree, estimate.allchars = TRUE,
                                  uncertainty.threshold = 0.95)
saveRDS(matrix_nodes, file = paste0("../data/processed/ancestral_states.", slug ,".Rda"))

## Add ancestral states to nodes
readRDS(paste0("../data/processed/ancestral_states.", slug ,".Rda"))
row.names(matrix_nodes) <- tree$node.label
matrix$matrix <- rbind(matrix$matrix, matrix_nodes)

## Constructing the distance matrix
matrix_dist <- MorphDistMatrixFast(matrix, distance = "Gower")
saveRDS(matrix_dist, file = paste0("../data/processed/distance_matrix.", slug ,".Rda"))
```

### 2017-11-27 analyses/02-time-slice-analyses.Rmd
Replace save and load with saveRDS and loadRDS, to prevent environment names issues

```{r}
## Loading the distance matrices
## See "01-extract-data-for analyses.Rmd" for how we made these
load(paste0("../data/processed/distance_matrix.", slug ,".Rda"))

@@

## Save results to output folder
save(out1, file = paste0("../outputs/age.", "Beck2014" ,".Rda"))

@@

## Save results to output folder
save(out2, file = paste0("../outputs/epoch.", slug ,".Rda"))
```

>>>>

```{r}
## Loading the distance matrices
## See "01-extract-data-for analyses.Rmd" for how we made these
readRDS(paste0("../data/processed/distance_matrix.", slug ,".Rda"))

@@

## Save results to output folder
saveRDS(out1, file = paste0("../outputs/age.", "Beck2014" ,".Rda"))

@@

## Save results to output folder
saveRDS(out2, file = paste0("../outputs/epoch.", slug ,".Rda"))
```
